Deployable Probabilistic Programming

### 2019-04-16 paper/paper.tex
in progress

\lstset{ % add your own preferences
    frame=none,
    basicstyle=\ttfamily\footnotesize,
    numbers=left,
    numbersep=5pt,
    showstringspaces=false,
    tabsize=4,
    language=Golang % this is it !
}

@@

Model:

\begin{lstlisting}
type Model struct {
    Data []float64
}

>>>>

\lstset{ % add your own preferences
    frame=none,
    basicstyle=\ttfamily\footnotesize,
    numbers=none,
    numbersep=5pt,
    showstringspaces=false,
    tabsize=4,
    language=Golang % this is it !
}

@@

Let us illustrate the use of Infergo on a basic example serving
as a probabilistic programming equivalent of the "Hello, World!"
program --- inferring parameters of a unidimensional Normal
distribution. In this example, the model holds the set of
samples from which the distribution parameters are to be
inferred:
\begin{lstlisting}
type Model struct {
    Data []float64
}
\end{lstlisting}
